\section{Future Work}
While we were able to answer many of our original questions, there are a number of open opportunites available to pursue as future work.

\subsection{Streaming Benchmarks}
While the Wordcount and Grep benchmarks provided interesting insights into Spark and System-X, neither was a particularly complicated streaming workload.  Key aspects of a typical streaming system, such as complicated sliding windows, joining multiple streams, or comparison to historical patterns were left out of these benchmarks.

One workload that would be particularly interesting is the canonical streaming benchmark, Linear Road.~\cite{linearroad}  Linear Road simulates the tracking of multiple "X-ways," each of which contains the continuously changing positions of multiple moving vehicles.  This benchmark is designed to test the full suite of streaming functionalities.

\subsection{Twitter Storm}
Twitter Storm is similar to Spark, another popular open source, main-memory distributed system.  While Storm has been compared less-than-favorably to Spark by Zaharia, et al~\cite{dstreams}, it would be interesting to see the same results from an unbiased source, particularly if a more complicated benchmark is used.

\subsection{Large-Scale Distribution}
While we were able to evaluate Spark on a small distributed system, realistic clusters of Spark machines include dozens, if not hundreds, of nodes.  We hypothesize that Spark continues to scale relatively linearly, as shown in their experiments.~\cite{dstreams}

\subsection{Distributed System-X}
One obvious omission from this paper is the lack of evaluation of System-X on a distributed environment.  We hypothesize that System-X would also scale linearly, though it is likely that there would be a reduction in throughput 

\subsection{S-Store}
S-Store is a new distributed, main-memory streaming system being developed as a collaboration between Brown University, MIT, and Brandeis University.  The current prototype of S-Store is built on the existing main-memory OLTP system, H-Store, and is designed to provide strong transactional guarantees on a streaming system.~\cite{hstore}  While it is highly unlikely that S-Store would beat Spark in a benchmarking comparison, it would be very interesting to see how the raw throughput numbers compare between systems with very different fundamental philosophies.  The specific question: can S-Store reach a streaming throughput comparable to Spark while also supporting OLTP?